---
title: "stock_volume_project"
output: github_document
date: "2026-03-11"
---

<h1>load packages</h1>
```{r}
library('tidyverse')
library('patchwork')
```

<h1>Read Data to dataframe</h1>
```{r}
df <- read.csv('ixic_aapl_amz_msft_stock_data.csv')
```

<h2>chaging column type of month_date</h2>
```{r}
df$month_date <- as.Date(df$month_date)
```




<h1>creating line plots to see volume, open, close, high, low, of aapl, msft, amazon, and IXIC stocks</h1>

<h2>line plots for volume</h2>
```{r}
plot1 <- ggplot(df)+
  geom_line(aes(x=month_date, y=volume))
plot2 <- ggplot(df)+
  geom_line(aes(x=month_date, y=volume_aapl))
plot3 <- ggplot(df)+
  geom_line(aes(x=month_date, y=volume_amazon))
plot4 <- ggplot(df)+
  geom_line(aes(x=month_date, y=volume_msft))
(plot1 + plot2)/(plot3 + plot4)
```
```{r}
smooth_plot1 <- ggplot(df)+
  geom_smooth(aes(x=month_date, y=volume))
smooth_plot2 <- ggplot(df)+
  geom_smooth(aes(x=month_date, y=volume_aapl))
smooth_plot3 <- ggplot(df)+
  geom_smooth(aes(x=month_date, y=volume_amazon))
smooth_plot4 <- ggplot(df)+
  geom_smooth(aes(x=month_date, y=volume_msft))
(smooth_plot1 + smooth_plot2)/(smooth_plot3 + smooth_plot4)
```




<h2>Seeing if months or seasons affect different stocks</h2>
<h3>aapl</h3>
```{r}
ggplot(df, aes(x=month_date, y=volume_aapl),na.rm=TRUE)+
  geom_line()+
  scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
  theme(axis.text.x = element_text(angle=90))
```
<h3>amazon</h3>
```{r}
ggplot(df, aes(x=month_date, y=volume_amazon),na.rm=TRUE)+
  geom_line()+
  scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
  theme(axis.text.x = element_text(angle=90))
```
<h3>msft</h3>


```{r}
ggplot(df, aes(x=month_date, y=volume_msft),na.rm=TRUE)+
  geom_line()+
  scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
  theme(axis.text.x = element_text(angle=90))
```
<h3>ixic index</h3>
```{r}
ggplot(df, aes(x=month_date, y=volume),na.rm=TRUE)+
  geom_line()+
  scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
  theme(axis.text.x = element_text(angle=90))
```
<h2>Making graphs to understand high, low, open, and close</h2>


```{r}
ggplot(df)+
  geom_line(mapping= aes(x=month_date, y=low))+
  geom_line(mapping= aes(x=month_date, y=high))+
  labs(title='IXIC index')+
    scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
    theme(axis.text.x = element_text(angle=90))
ggplot(df)+
  geom_line(mapping= aes(x=month_date, y=low_aapl))+
  geom_line(mapping= aes(x=month_date, y=high_aapl))+
  labs(title='apple')+
    scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
    theme(axis.text.x = element_text(angle=90))
ggplot(df)+
  geom_line(mapping= aes(x=month_date, y=low_amazon))+
  geom_line(mapping= aes(x=month_date, y=high_amazon))+
  labs(title='amazon')+
    scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
    theme(axis.text.x = element_text(angle=90))
ggplot(df)+
  geom_line(mapping= aes(x=month_date, y=low_msft))+
  geom_line(mapping= aes(x=month_date, y=high_msft))+
  labs(title='microsoft')+
    scale_x_date(
    date_breaks = '1 month',
    date_labels = '%b %Y'
  )+
    theme(axis.text.x = element_text(angle=90))

  
```
<h1>checking for correlation with stock price and volume</h1>


```{r}
cor_ixic <- cor(df$volume,df$close)
ggplot(df,aes(x=volume,y=close))+
  geom_point()+
  labs(title=paste('IXIC Index---',cor_ixic))

cor_aapl <- cor(df$volume_aapl,df$close_aapl)
ggplot(df,aes(x=volume_aapl,y=close_aapl))+
  geom_point()+
  labs(title=paste('apple---',cor_aapl))

cor_amazon <- cor(df$volume_amazon,df$close_amazon)
ggplot(df,aes(x=volume_amazon,y=close_amazon))+
  geom_point()+
  labs(title=paste('amazon---',cor_amazon))

cor_msft <- cor(df$volume_msft,df$close_msft)
ggplot(df,aes(x=volume_msft,y=close_msft))+
  geom_point()+
  labs(title=paste('microsoft---',cor_msft))

  

```
<h1>calculating volatility</h1>
<h3>creating percent volatility columns</h3>
```{r}
df$volatility <- ((df$high - df$low) / df$open) * 100
df$volatility_aapl <- ((df$high_aapl - df$low_aapl) / df$open_aapl) * 100
df$volatility_amazon <- ((df$high_amazon - df$low_amazon) / df$open_amazon) * 100
df$volatility_msft <- ((df$high_msft - df$low_msft) / df$open_msft) * 100

```

<h3>calculating average volatility between the different stocks</h3>
```{r}
mean(df$volatility)
mean(df$volatility_aapl)
mean(df$volatility_amazon)
mean(df$volatility_msft)
```
<h3>graphing volatility</h3>
```{r}
ggplot(df)+
  geom_line(mapping=aes(x=month_date, y=volatility), color='blue',linewidth=2)+
  geom_line(mapping=aes(x=month_date, y=volatility_aapl),color='purple',linewidth=2)+
  geom_line(mapping=aes(x=month_date, y=volatility_amazon),color='red',linewidth=2)+
  geom_line(mapping=aes(x=month_date, y=volatility_msft),color='green',linewidth=2)

```

<h1> normalized volume </h1>


```{r}
df$normalized_volume <- (df$volume / df$volume[1]) * 100
df$normalized_volume_aapl <- (df$volume_aapl / df$volume_aapl[1]) * 100
df$normalized_volume_amazon <- (df$volume_amazon / df$volume_amazon[1]) * 100
df$normalized_volume_msft <- (df$volume_msft / df$volume_msft[1]) * 100
ggplot(df)+
  geom_line(mapping = aes(x=month_date, y=normalized_volume))+
  geom_line(mapping = aes(x=month_date, y=normalized_volume_aapl))+
  geom_line(mapping = aes(x=month_date, y=normalized_volume_amazon))+
  geom_line(mapping = aes(x=month_date, y=normalized_volume_msft))
ggplot(df)+
  geom_smooth(mapping = aes(x=month_date, y=normalized_volume))+
  geom_smooth(mapping = aes(x=month_date, y=normalized_volume_aapl))+
  geom_smooth(mapping = aes(x=month_date, y=normalized_volume_amazon))+
  geom_smooth(mapping = aes(x=month_date, y=normalized_volume_msft))
```







